\section*{Abstract}

The Student Life Support Service is a web application developed to streamline student support processes at the Vietnamese-German University (VGU). The system addresses the needs of students, dormitory staff, and administrators by facilitating efficient communication and ticket management for daily student life issues. \\ \\
The key objectives of this project are to enhance student-staff interaction, simplify ticket resolution, and improve the overall support experience. Students can create, view, and manage support tickets, while staff members handle ticket processing and communication with students. Administrators oversee the entire system, managing users, roles, and system reports. \\ \\
The application is built using a modern technology stack. The frontend, developed with ReactJS, Material \acs{ui}, and Vite, incorporates a responsive design that ensures compatibility with various devices, including desktops, laptops, tablets, and smartphones. This ensures that users have a seamless experience regardless of the device they are using. The backend is powered by NodeJS, ExpressJS, and SocketIO for real-time communication, with \acs{jwt}-based authentication (utilizing access and refresh tokens stored in a Redis in-memory database). The system's data is managed using PostgreSQL for robust and scalable database management. \\ \\
The project adopts a modular and \acs{rest}ful \acs{api}-driven architecture to facilitate scalability and maintainability. The methodology involves iterative development with thorough testing at each stage to ensure the system meets functional and performance requirements. \\ \\
Preliminary results indicate that the Student Life Support Service significantly improves the efficiency of support ticket management and fosters better communication between students and university staff. The system's modular design and responsiveness enable future enhancements, making it adaptable to evolving requirements at VGU.