\section*{Acknowledgments}

% \begin{flushright}
%     Hello 
% \end{flushright}

%First and foremost, I wish to convey my deepest gratitude to the distinguished faculty at the Vietnamese-German University and Frankfurt University of Applied Science. Their steadfast guidance and support have been pivotal in my academic and personal development throughout my four-year undergraduate studies. \\ \\
%Secondly, I wish to express my sincere gratitude to Mr. Nguyen Son Giang, my esteemed manager, for his invaluable guidance and unwavering support throughout the duration of my academic pursuit. His mentorship has been instrumental in enabling me to explore and develop my skills in the domain of Web Development, while also fostering a deep and lasting interest in this field. \\ \\
%Furthermore, I wish to extend my profound gratitude to all members of the Web Development team for their invaluable assistance throughout my internship. Their insights, suggestions, and feedback have been instrumental in shaping my learning experience. I deeply appreciate their unwavering patience and support, which have significantly contributed to my professional growth.


First and foremost, I would like to extend my heartfelt gratitude to my two supervisors, Dr. Tran Hong Ngoc and Mr. Truong Dinh Huy, for dedicating their valuable time and effort to review and provide feedback on my thesis. Working closely with Dr. Tran Hong Ngoc over the years has made me appreciate her constant enthusiasm and approachable nature, which significantly boosted my confidence and comfort in completing this work. She was always available to offer guidance and constructive feedback whenever I needed assistance. \\ \\
Moreover, I am also deeply thankful to the dedicated \ac{cse} assistants, whose thorough guidance throughout the thesis process and patience in addressing my questions were invaluable to my research. \\ \\
Lastly, I want to express my sincere appreciation to all the lecturers at \ac{vgu} and Frankfurt University of Applied Sciences, whose teachings and guidance have been instrumental in shaping my academic journey. I am also incredibly grateful to my friends and family, whose unwavering support and encouragement have been a constant source of strength throughout my four years of study. \\ \\