\section{Internship Result}

\subsection{Internship target and expectation}

During my internship at BGSW Vietnam, my primary target was to bridge the gap between theoretical knowledge and practical application in the realm of web application development. I aimed to gain hands-on experience with industry-standard tools and technologies, such as Python, Flask, SQLAlchemy, and front-end frameworks. My expectations included enhancing my programming skills, understanding the full software development lifecycle, and learning to collaborate effectively within a team environment. Additionally, I sought to develop strong problem-solving abilities by tackling real-world challenges and to understand the best practices for code quality, testing, and deployment. I also anticipated gaining insights into agile methodologies and improving my ability to manage tasks and timelines efficiently. Overall, my goal was to emerge from this internship with a solid foundation in web application development and a clear understanding of the dynamics of working in a professional software development setting.

\subsection{Internship output}

Upon completing my internship at BGSW Vietnam, I have successfully achieved and exceeded my initial targets and expectations. I played a crucial role in the development of a comprehensive web application project, contributing significantly to both backend and frontend development. I developed proficiency in utilizing the Flask framework to build robust APIs, and I enhanced my skills in database management with SQLAlchemy. I also gained experience with version control using Git, and I learned how to use Docker for containerization, ensuring that our development environment was consistent and scalable. My problem-solving skills were honed as I addressed various technical challenges, such as optimizing database queries and handling concurrency issues. The internship also provided me with valuable experience in writing documentation, including API documentation with Swagger and setup guides for deployment. The positive feedback from my mentors and peers, along with the successful completion of project milestones, indicates that I have made a substantial contribution to the team. This experience has significantly boosted my confidence in my technical and collaborative abilities.

\subsection{Future path}
My immediate goal is to secure a software developer position where I can continue to refine my skills and contribute to impactful projects. I am particularly interested in roles that involve web application development, cloud computing, and data management, as these areas align with the expertise I developed during my internship. In the long term, I aspire to become a full-stack developer, capable of designing and implementing complex applications from front-end to back-end. I plan to pursue continuous learning through professional development courses, certifications, and staying updated with emerging technologies and industry trends. Additionally, I am motivated to contribute to open-source projects and participate in tech communities to broaden my knowledge and network. Ultimately, I aim to leverage my skills to create innovative solutions that address real-world problems, drive business success, and enhance user experiences.




