\section{Conclusion}

This report presents the outcomes of the internship program undertaken at BGSW Vietnam, selected to fulfill the practical training requirements as an IT Developer. Throughout the internship duration, active involvement in technical skills training and engagement in the web application project constituted significant aspects of the experience. This comprehensive training encompassed various facets of software development, from backend and frontend programming to database design and system integration, providing a holistic view of the development lifecycle. \\

\noindent Engagement in the web application project was particularly enriching. It allowed for the application of theoretical knowledge to real-world scenarios, enhancing my problem-solving abilities and technical proficiency. Working on tasks such as designing database schemas, implementing API endpoints, and optimizing query performance offered practical insights into the complexities of software development. The collaborative environment at BGSW Vietnam further augmented my learning, as I received constructive feedback from mentors and collaborated with team members, fostering an atmosphere of continuous improvement. \\

\noindent The amalgamation of these factors facilitated a rich and rewarding experience within the scope of the internship program. The skills and knowledge acquired during this period have significantly bolstered my readiness to tackle professional challenges in the software development field. The internship at BGSW Vietnam has not only solidified my technical foundation but also instilled a sense of confidence and preparedness to contribute effectively to future projects. As I move forward, the experiences and lessons learned during this internship will undoubtedly serve as a cornerstone for my career development, guiding me in my journey as an aspiring software developer.